Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-30 paper/aldebaran.tex
wording

$\gamma$~Draconis (also known as Eltanin, or $\gamma$~Dra) is a second-magnitude K5III giant which had been observed by \citet{hatzes1993} as part of the same campaign that led to the discovery of Aldebaran~b and Pollux~b. \citet{2018arXiv180105239H} have recently shown that the 702~d period RV variations of the putative Eltanin~b disappeared from 2011-2013, returning in 2014 with a different amplitude and phase. They ascribe this to the beating between two modes of a previously-unidentified kind of stellar variability, and warn that ``Given that the periods found in $\alpha$~Tau [Aldebaran] are comparable to those in $\gamma$~Dra and both stars are evolved with large radii, a closer scrutiny of the RV variability of $\alpha$~Tau is warranted.''

>>>>

$\gamma$~Draconis (also known as Eltanin, or $\gamma$~Dra) is a second-magnitude K5III giant which had been observed by \citet{hatzes1993} as part of the same campaign that led to the discovery of Aldebaran~b and Pollux~b. \citet{2018arXiv180105239H} have recently shown that the 702~d period RV variations of the putative Eltanin~b disappeared from 2011-2013, returning in 2014 with a different amplitude and phase. They ascribe this to a previously-unidentified kind of stellar variability, and warn that ``Given that the periods found in $\alpha$~Tau [Aldebaran] are comparable to those in $\gamma$~Dra and both stars are evolved with large radii, a closer scrutiny of the RV variability of $\alpha$~Tau is warranted.''
